Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-08 paper.tex
Updates to background.

Collaboration as learning

Collaboration as decision-making

Collaboration as consensus

Collaboration as community

Collaboration and social capital

Networked collaboration: theory

Networked collaboration: experiment

@@

Social learning on networks has been studied extensively
\cite{mobius_social_2014},
focusing on how networked agents can aggregate noisy measurements of
a ``true'' value.
In this setting, a naive Bayesian approach converges to the true value when
certain conditions on degree distribution are met,
with the speed of convergence depending on the network's {\em spectral gap},
the gap between the largest two eigenvalues of its adjacency matrix
\cite{golub_naive_2010}.
In other settings, collaboration is better modeled as a problem
of finding the global maximum of a multi-peaked payoff function.
In this case, lab experiments have shown a complex relationship between
convergence time, solution quality, with the efficacy of different
network types (fully-connected, ring, small-world, etc.)
varying depending on the parameters of the payoff function
\cite{mason_propagation_2008}.

@@

A number of theoretical and lab experiments have evaluated the role of networks
in collective decision-making.
Some studies focus on how network structure influences individual tendency
towards altruistic decisions, rather than on decisions made by an entire
group \cite{eshel_altruists_1998}.
Grim et al. \cite{grim_scientific_2013} simulated the performance of decision-makers
seeking to maximize an objective function by communicating their values on a
number of network structures, observing another tradeoff between speed (for the
fully-connected network) and quality (for a ring network).
Grim et al. also found that speed correlated with the characteristic path length
when running their simulations on parameterized small-world networks
\cite{watts_collective_1998}.

Lab-based experiments suggest a complex interaction between network topology
and other factors.
While groups of networked human subjects reliably perform very well on
difficult graph-coloring tasks, the best performing network architectures
(e.g., fully-connected vs. small-world) vary
from task to task \cite{kearns_experiments_2012}.
The same studies found that while human subjects tend to perform very well on
a number of networks, they perform worst on collaboratively self-organized
networks, highlighting the importance of intentionality
in constructing communication channels for collective decision-making.
Similarly, some network topologies are able to reach faster decisions in the
presence of more information, while others show the opposite effect
\cite{kearns_experimental_2006}.
Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
suggest that individual decisions towards altruism are conditional on their
neighbor's behavior and ``contagious'' up to three degrees away.
Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
existence of conditional altruism,
but disconfirmed the three-degree hypothesis and conlcuded that altruistic
behavior only influences first-degree neighbors.

@@

We also introduce local variants of these strategies.
The local variants are meant to reflect a more realistic collaboration setting where
individual agents focus on sub-problems.
In these variants, individual learning takes place on a subset of NK loci.
Each agent is associated with an NK locus and the loci its value depends on.
These loci are the agent's {\em concern},
and are the only ones used for individual learning.
Similarly, in the consensus strategy, an NK locus's value is determined only by the agents
concerned with that locus, rather than all agents.

>>>>

In the field of social learning,
much research has been done to understand how groups of agents
can solve problems collaboratively.
In {\em networked social learning}, agents are represented by nodes on a network
and can only interact with their neighbors.
Social learning tasks can be divided into cases where agents have {\em generated signals}
(independently noisy estimates of a true value)
and those where agents have {\em interpreted signals}
(solutions based on different internal models of available data)
\cite{hong_interpreted_2009}.
For generated signals,
a naive Bayesian approach converges to the truth when conditions
on the network's degree distribution,
while the speed of convergence depends on the {\em spectral gap}
between the two largest eigenvalues of the network's adjacency matrix
\cite{golub_naive_2010}.
Complex social learning tasks can also be modeled as the problem
of maximizing an objective function with many local maxima,
referred to as a {\em rugged landscape}
\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
Numerical simulations have shown ttht efficient networks (those with short paths between nodes)
can allow less exploration of possible solutions,
resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008, grim_scientific_2013}.
However, when conformity-based social learning strategies are used, efficient networks can outperform
inefficient ones \cite{barkoczi_social_2016}.

Lab-based experiments on networked collaboration
suggest a complex interaction between network topology,
and other factors.
While groups of networked human subjects reliably perform very well on
difficult graph-coloring tasks, the best performing network architectures
(e.g., fully-connected vs. small-world) vary
from task to task \cite{kearns_experiments_2012}.
The same studies found that while human subjects tend to perform very well on
a number of networks, they perform worst on collaboratively self-organized
networks, highlighting the importance of intentionality
in constructing communication channels for collective decision-making.
Similarly, some network topologies are able to reach faster decisions in the
presence of more information, while others show the opposite effect
\cite{kearns_experimental_2006}.
Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
suggest that individual decisions towards altruism are conditional on their
neighbor's behavior and ``contagious'' up to three degrees away.
Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
existence of conditional altruism,
but conlcuded that altruistic
behavior only influences first-degree neighbors.

Collaboration as decision-making
Collaboration as consensus

Collaboration as community
Collaboration and social capital

Collaboration on Wikipedia

@@

OLD STUFF BELOW HERE

@@

@@

We also introduce local variants of the above strategies.
The local variants are meant to reflect a more realistic collaboration setting where
individual agents focus on sub-problems.
In these variants, individual learning takes place on a subset of NK loci.
Each agent is associated with an NK locus and the loci its value depends on.
These loci are the agent's {\em concern},
and are the only ones used for individual learning.
Similarly, in the consensus strategy, an NK locus's value is determined only by the agents
concerned with that locus, rather than all agents.
